{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-08-05 wacv_for_review.tex
Figures Updated - Text Cleaned

\begin{figure*}[!h]
\centering
\includegraphics[width=0.70\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure*}

@@

@@

\begin{figure*}[h]
\centering
\begin{tabular}{ccc}
\tiny\quad\textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure*}

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.
\begin{table*}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

@@

\textbf{Deep Learning Features} Our focus so far was to build a high speed tracker
that can run about 30fps on a low-end hardware. In this direction, we used HoG and
color features in an efficient way in the proposed {\it E}nKCF tracking concept. Deep Learning
features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF tracker can run more reliably with deep learning
features on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
the first convolutional layer features lead to slightly better precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the third convolutional layer
features to get the response map. In the next stage, they use the translation estimation from the first stage to
employ second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
position estimated in the second stage. This coarse-to-fine position estimation approach allows embedding 
more representative features of the object. However, such approach requires multiple runs of a KCF at a single
frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
deep learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different feature representations. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers at more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[t]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.50cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.47\textwidth]{./figures/Filters_Details.pdf}
\caption{Examples of three filters; the translation filter,
  \textit{target+small background}, the scale filter,
  \textit{target-only} and another translation filter,
  \textit{target+large background}, and their Hanning window and
  expected Gaussian response.}
\label{fig:Filters}
\end{figure}

@@

\begin{figure*}[h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\hspace{.37\linewidth}\textbf{OTB100}\\
\includegraphics[width=3.30cm]{./figures/pr_uav123.eps}
\includegraphics[width=3.55cm]{./figures/sr_uav123.eps}
\includegraphics[width=3.30cm]{./figures/pr_otb100.eps}
\includegraphics[width=3.55cm]{./figures/sr_otb100.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure*}

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

@@

\begin{table*}[h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table*}

\textbf{Evaluation with Deep Features} Our focus so far was to build a high speed object tracker
that can run at about 30fps on a low-end hardware. In this direction, we used HoG and
color features in an efficient way in the proposed {\it E}nKCF. Deep
features, on the other hand, recently have been proved to boost tracking accuracy \cite{ma2015hierarchical,
danelljan2015convolutional}. For this reason, we believe that, the {\it E}nKCF can run more reliably with deep learning
features at the targeted frame rate on the more sophisticated platforms (GPUs). \cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer features of the VGGNet \cite{simonyan2014very}. Their experiments showed that
the first convolutional layer features lead to slightly better precision and success rates than the second
layer. \cite{ma2015hierarchical} proposed a KCF tracker with deeper features. Their method employs the activations of third convolutional layer
features to get the response map. In the next stage, they use the translation estimation from the first stage to
employ the second convolutional layer features. Finally, the first convolutional layer features is extracted from the 
position estimated in the second stage. This coarse-to-fine tracking approach allows embedding 
more representative features of the object, however, such approach requires multiple runs of a KCF at a single
frame, increasing the run-time complexity. For this reason, we follow a similar approach to \cite{danelljan2015convolutional} to embed
deep learning features.

Our {\it E}nKCF framework provides us flexibility to exploit different level of abstractions in different KCFs. The translation filters, $R_{t}^{L}$ and $R_{t}^{S}$, 
considers more than twice larger area than $R_{s}$. Taking this into account, we can assign deeper feature encodings to $R_{s}$ as it requires less
spatial information than  $R_{t}^{L}$ and $R_{t}^{S}$. Hence, we assign the activations of the fourth convolutional layer features ($26\times26\times128$) to $R_{s}$  whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the activations of the second layer features ($109\times109\times64$). This feature assignment is represented as  \textit{conv224-VGG} and shown in fig.~\ref{fig:Filters_CNN}. Additionally, we assign the second convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and $R_{t}^{S}$ and compare this setting  (\textit{conv222-VGG}) to  \textit{conv224-VGG}. We use the VGGNet as it provides higher spatial resolution at the first layers than than AlexNet \cite{krizhevsky2012imagenet}.

@@

\begin{figure}[t]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with deep features and HoG and Color features.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
